---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# worldcities

<!-- badges: start -->
<!-- badges: end -->

`worldcities` contains a dataset of 40,000 cities and associated metadata such as coordinates, country, and population. 

## Installation

You can install the released version of worldcities from github with:

``` r
remotes::install_github("condwanaland/worldcities")
```


## Example

To use `worldcities` first load it with `library()`

```{r example}
library(worldcities)
```

You can then access the dataset by just calling `worldcities`

```{r}
wc <- worldcities
head(wc)
```

You can then use this in any further analyses

```{r}
library(ggplot2)
library(rnaturalearth)
library(rnaturalearthdata)

# This grabs a map of the world from the `rnaturaldata` packages
world <- ne_countries(scale = "medium", returnclass = "sf")

ggplot(data = world) +
    geom_sf() +
    geom_point(data = worldcities, aes(x = lng, y = lat, size = population), 
        shape = 23, fill = "darkred", alpha = 0.1) +
    coord_sf()

```
There's way too much data to get anything meaningful from this view, but it does give you an idea of the areas this dataset covers. 

## License

Data for this package comes from SimpleMaps (https://simplemaps.com/data). The World Cities data is released under a CCBY license which is preserved here. The original, raw data can be found here (https://simplemaps.com/data/world-cities).

